---
title: "Eating Behavior Data Cleaning"
author: "Katherine"
date: "2/3/2022"
output: html_document
---


Load scorekeeper, sjmisc, haven, readxl, set working directory to the project directory
```{r, setup, echo = FALSE, message=FALSE}
library(scorekeeper)
library(sjmisc)
library(haven)
library(readxl)
library(cgwtools)
library(dplyr)

```

Load Raw Data file
```{r, results='hide'}
ALSPAC_raw <- read_spss('ALSPAC.Raw.sav') %>% 
  filter(qlet == 'A')
```

Load Binge Eating Scoresheet
```{r, echo = TRUE}
binge_score <- read_excel('scoresheets/binge_scoresheet_ALSPAC.xlsx')
```

Score binge eating data and save as 'binge_eating' 
```{r, echo = TRUE, warning=FALSE}
binge_scored <- scorekeep(ALSPAC_Raw, binge_score)
binge_eating <- binge_scored[[8]]
resave(binge_eating, file = 'ALSPAC_Cleaned.RData')
```

Load Compensatory Scoresheet    
```{r}
comp_score <- read_excel('data_cleaning/scoresheets/compensatory_scoresheet_ALSPAC.xlsx')
```

Score behaviors data and save as 'compensatory_behaviors' in the cleaned data file
```{r, warning=FALSE}
comp_scored <- scorekeep(ALSPAC_raw, comp_score)
compensatory_behaviors <- comp_scored [[5]]
resave(compensatory_behaviors, file = 'ALSPAC_Cleaned.RData')
```

Load Driven Exercise Scoresheet
```{r}
driven_ex_score <- read_excel('scoresheets/driven_ex_scoresheet_ALSPAC.xlsx')
```

score driven exercise data and save as 'driven exercise' in the cleaned data file
```{r, warning=FALSE}
ex_scored <- scorekeep(ALSPAC_raw, driven_ex_score)
driven_exercise <- ex_scored [[7]]
resave(driven_exercise, file = 'ALSPAC_Cleaned.RData')
```
