---
title: "Dieting at age 14"
output: html_document
---
##Background
The dieting at age 14 questionnaire is a set of two questions asked as a part of the ALSPAC study. Data from these questions has been used in multiple studies...(insert links). The two questions aim to learn the extent of dieting a respondent has taken part in. The first question asks the frequency of dieting and the second question asks about the length of diets in the past year.

##Scoresheet
1. The ID and raw variables are added to the scoresheet first
2. Create an unskipped variable to remove respondents without dieting behavior 
3. Recode the variables to align with lab standards
4. Select the final 3 variables
5. Run the Scorekeeper function with the raw data and the completed scoresheet

##Key Variables
`diet_freq.14`
`diet_length.14`

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '/Volumes/data/Embark Lab/ALSPAC/Data/')
```

```{r, echo = false}
library (haven)
library (scorekeeper)
library (readxl)

alspac_raw <- read_spss('../ALSPAC.Raw.sav')

dieting_14_scoresheet <- read_excel("../scoresheets/ED_cognitions_individual_sheets/dieting_14_scoresheet.xlsx")

scorekeep (alspac_raw, dieting_14_scoresheet)
```
