---
title: "Emotional Eating at Age 14"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
bibliography: references.bib
---

## Background

Scoring of the ALSPAC Emotional Eating Scale at age 14 This scale was
developed as part of the Dutch Eating Behaviors Questionnaire
(DEBQ)[@vanstrien1986] and has been used in multiple studies
[@nolan2012] [@snoek2007] . The Emotional Eating scale is made up of 14
items each of which represent a different emotional state. The scale
asks respondents the frequency which they respond to a specific
emotional state by consuming more food, ranging from "no, not at all"
(1), "yes, usually" (1), "yes, sometimes" (2).

## Scoresheet

The full scoresheet can be found here [emo_eat_14](/emo_eat_14.xlsx)

The 14 raw variables were renamed and recoded to better align with the
response scale. "no, not at all" was set to 0, "yes, sometimes" was set
to 1, and "yes, usually" was set to 2. A new set of dichotimized
variables was created for the 14 raw variables. Finally sums were
created for both the raw and dichotimized variables.

## Key Variables

Key Variables include the 14 original variables recoded, the sum of the
original variables, as well as the sum of the 14 dichotomized variables.

`emo_eat_irritated.14` 

`emo_eat_nothingtodo.14` 

`emo_eat_depressed.14`

`emo_eat_lonely.14` 

`emo_eat_letdown.14` 

`emo_eat_happy.14`

`emo_eat_unpleasent.14` 

`emo_eat_anxious.14` 

`emo_eat_wrong.14`

`emo_eat_freight.14`

`emo_eat_dissapoint.14` 

`emo_eat_upset.14`

`emo_eat_bored.14` 

`emo_eat_excited.14` 

`emo_eat_sum.14`

`emo_eat_sum_d.14`

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '/Volumes/data/Embark Lab/ALSPAC/Data')
```

```{r, echo=FALSE}
library(haven)
library (readxl)
library(cgwtools)

alspac_raw<- read_sav("AlSPAC.Raw.sav")

emo_eat_14 <- read_excel("scoresheets/ED_cognitions_individual_sheets/emo_eat_14.xlsx")
View(emo_eat_14)

library(scorekeeper)
scored_emo_eat_14 <- scorekeep(ALSPAC_Raw, emo_eat_14)

#emotional_eating_14 <- ____[[6]]
#resave(body_dissatisfaction, file = 'ALSPAC_Cleaned.RData')
```
