---
title: "Body Satisfaction at age 14 R markdown"
output:
  html_document:
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
bibliography: references.bib
---

Scoring of the ALSPAC Body Satisfaction Scale at age 14 This scale is an
adaptation of the Satisfaction and Dissatisfaction with Body Parts Scale
the adaptation was developed by Eric Stice. [@Stice] It has been used in
ALSPAC in the following studies [@Bornioli.2019, @Bornioli.2021] An 11
item scale where one item differs between the sexes, two items grade
overall body satisfaction (`body_sat_weight.14`, `body_sat_figure.14`)
while the other nine refer to specific body parts (`body_sat_build.14`,
`body_sat_breasts.14`, `body_sat_stomach.14`, `body_sat_waist.14`,
`body_sat_thighs.14`, `body_sat_buttocks.14`, `body_sat_hips.14`,
`body_sat_legs.14`, `body_sat_face.14`, `body_sat_hair.14`). Graded on a
5 point likert scale from "Extremely Satisfied" (1) to "Extremely
Dissatisfied" (5) Body dissatisfaction was determined with the mean
score of all items using one different item in boys vs. girls, with
higher scores indicating higher body dissatisfaction.

Key Variables for Body Dissatisfaction at age 14 are:

`body_sat_weight.14`

`body_sat_figure.14`

`body_sat_build.14`

`body_sat_breasts.14`

`body_sat_stomach.14`

`body_sat_waist.14`

`body_sat_thighs.14`

`body_sat_buttocks.14`

`body_sat_hips.14`

`body_sat_legs.14`

`body_sat_face.14`

`body_sat_hair.14`

`body_sat_mean.14`

`body_sat_mean_NAs.14`

First we Load the Raw Data

```{r}
library(haven)
library (readxl)
library(scorekeeper)
library(cgwtools)

load("body_dissat_test.RData")
```

and then we load the scoresheet

```{r}

body_sat_score <- read_excel("scoresheets/body_dissastisfaction_scoresheet_ALSPAC.xlsx") 
View(body_sat_score)
```

Now we Load in the scorekeeper package and run the scorekeep function

```{r}


scored_body_sat <- scorekeep(body_dissat, body_sat_score)
scored_body_sat
```

now we will save this into the body satisfaction cleaned data

```{r}
body_dissatisfaction <- scored_body_sat[[6]]
resave(body_dissatisfaction, file = 'ALSPAC_Cleaned.RData')
```

```{r}
scored_body_sat
```

We now have 15 variables the original raw variables, ID, participant
sex, and the means of participant responses. because boys and girls
received one different item on the scale we expect each participant to
be missing one value.
